conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-16 paper/paper.Rmd
Updated conclusion section
Added an abstract
Updated abstract

# Summary

@@

However, there were major limitations with the methods in @prem2021. First, not all countries were included in their analyses. Second, some of the synthetic contact matrices did not have enough granularity; they covered a large area, such as "urban" or "rural" for a given country. This is disadvantegous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality. Third, the methodology used by Prem et al. was challenging to reuse in other contexts. Prem et al. provided the code used for their analysis, but that code was not designed for replicability and user-defined inputs.

The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government. We created methods and software to facilitate the following:

@@

# Future Work

>>>>

# Abstract

This article introduces `conmat`, an R package which generates synthetic contact matrices.

There are currently few options to generate synthetic contact matrices with existing contact surveys. 
Existing methods to generate synthetic contact matrices are not designed for replicability, do not have enough granularity, and does not cover enough administrative areas (some countries are not included).

A higher level of granularity however is sometimes required to make public health decisions for a given population.

[ What's different and useful about conmat? ]

[ What else is covered in this paper? ] The implemented methods are tested and an example of its use is provided for a local government area (i.e. sub-national level) in Australia.

# Motivation / Introduction

@@

However, there were major limitations with the methods in @prem2021. First, not all countries were included in their analyses. Second, some of the synthetic contact matrices did not have enough granularity; they covered a large area, such as "urban" or "rural" for a given country. This is disadvantegous as public health groups might need to make predictions for more fine-grained areas within a country, such as a district or municipality. Third, the methodology used by Prem et al. was challenging to reuse in other contexts. Prem et al. provided the code used for their analysis, but that code was not designed for replicability and use with user-defined inputs.

[REVISED PARAGRAPH BELOW] The `conmat` package was created to fill a specific need for creating synthetic contact matrices for specific local government areas for Australia, for work commissioned by the Australian government. We created methods and software to facilitate the following:

@@

# Conclusions and Future Direction
